---
title: "Word cloud for 15 days after the incident across categories"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE}
memory.limit(100000)
library(ggplot2) # Data visualization
library(ggdendro)
library(readr) # CSV file I/O, e.g. the read_csv function
library(tm) # Package for text mining
library(SnowballC)
library(wordcloud)
library(dplyr)
library(gridExtra)
library(RColorBrewer) # Data Visualization
library(openNLP)
library(koRpus)
library(Rstem)
library(lsa)

wcloud_Ashley <- function(documents){
     documents = gsub("[^a-zA-Z0-9 ]", "", documents)
    documents= gsub("[[:digit:]]", "",documents)
    documents= gsub("http\\w+", "", documents)
    documents = gsub("\n", "", documents)  
    wordcorpus <- Corpus(VectorSource(documents)) %>% 
    tm_map(content_transformer(tolower)) %>%
    #tm_map(stemDocument,language = "english") %>% 
    tm_map(removePunctuation) %>%
    tm_map(stripWhitespace) %>% 
    tm_map(removeWords,stopwords("english")) %>%
    tm_map(removeWords,
           c("Ashley Madison","ashleymadison","madison","madisons","ashley","http","website","hack","hacking","hackers","hacked","site","hacks",
             "WWW","twitter")) %>%
    DocumentTermMatrix() %>%
    as.matrix() %>%
    as.data.frame()
  return(wordcorpus)
} 
wcloud_Snowden <- function(documents){
     documents = gsub("[^a-zA-Z0-9 ]", "", documents)
    documents= gsub("[[:digit:]]", "",documents)
    documents= gsub("http\\w+", "", documents)
    documents = gsub("\n", "", documents)  
    wordcorpus <- Corpus(VectorSource(documents)) %>% 
    tm_map(content_transformer(tolower)) %>%
    #tm_map(stemDocument,language = "english") %>% 
    tm_map(removePunctuation) %>%
    tm_map(stripWhitespace) %>% 
    tm_map(removeWords,stopwords("english")) %>%
    tm_map(removeWords,
           c("edward snowden","snowden","snowdens","hong","hero","kong","edward","http","website","nsa","cia",
             "WWW","twitter")) %>%
    DocumentTermMatrix() %>%
    as.matrix() %>%
    as.data.frame()
  return(wordcorpus)
} 

wcloud_Celeb <- function(documents){
     documents = gsub("[^a-zA-Z0-9 ]", "", documents)
    documents= gsub("[[:digit:]]", "",documents)
    documents= gsub("http\\w+", "", documents)
    documents = gsub("\n", "", documents)  
    wordcorpus <- Corpus(VectorSource(documents)) %>% 
    tm_map(content_transformer(tolower)) %>%
    #tm_map(stemDocument,language = "english") %>% 
    tm_map(removePunctuation) %>%
    tm_map(stripWhitespace) %>% 
    tm_map(removeWords,stopwords("english")) %>%
    tm_map(removeWords,
           c("photo", "hack","celebrity", "nude","celeb","http","website",
             "WWW","twitter","nudephoto","icloud","apple","fbi","hacking")) %>%
    DocumentTermMatrix() %>%
    as.matrix() %>%
    as.data.frame()
  return(wordcorpus)
} 

wcloud_Apple <- function(documents){
     documents = gsub("[^a-zA-Z0-9 ]", "", documents)
    documents= gsub("[[:digit:]]", "",documents)
    documents= gsub("http\\w+", "", documents)
    documents = gsub("\n", "", documents)  
    wordcorpus <- Corpus(VectorSource(documents)) %>% 
    tm_map(content_transformer(tolower)) %>%
    #tm_map(stemDocument,language = "english") %>% 
    tm_map(removePunctuation) %>%
    tm_map(stripWhitespace) %>% 
    tm_map(removeWords,stopwords("english")) %>%
    tm_map(removeWords,
           c("fbi","apple","encryption","fbiv.apple","fbivsapple","http","website",
             "WWW","twitter","apples","says","iphone","appleencryptionfbi","appleremember","new","york","say","via","good")) %>%
    DocumentTermMatrix() %>%
    as.matrix() %>%
    as.data.frame()
  return(wordcorpus)
} 


Ash2=read.csv("C:/Users/Jay/Desktop/Prof.Mike/Ashley Madison/Ash2.csv",stringsAsFactors = FALSE)

Ash2_Neutral=Ash2[Ash2$Category=="Basic Neutral",]
Ash2_Positive=Ash2[Ash2$Category=="Basic Positive",]
Ash2_Negative=Ash2[Ash2$Category=="Basic Negative",]

Snow1=read.csv("C:/Users/Jay/Desktop/Prof.Mike/Snowden/Snow1.csv",stringsAsFactors = FALSE)
Snow2=read.csv("C:/Users/Jay/Desktop/Prof.Mike/Snowden/Snow2.csv",stringsAsFactors = FALSE)
Snow2=rbind(Snow1,Snow2)

Snow2_Neutral=Snow2[Snow2$Category=="Basic Neutral",]
Snow2_Positive=Snow2[Snow2$Category=="Basic Positive",]
Snow2_Negative=Snow2[Snow2$Category=="Basic Negative",]

Celeb2=read.csv("C:/Users/Jay/Desktop/Prof.Mike/Celeb photo hack/Celeb2.csv", stringsAsFactors = FALSE)

Celeb2_Neutral=Celeb2[Celeb2$Category=="Basic Neutral",]
Celeb2_Positive=Celeb2[Celeb2$Category=="Basic Positive",]
Celeb2_Negative=Celeb2[Celeb2$Category=="Basic Negative",]

Apple2=read.csv("C:/Users/Jay/Desktop/Prof.Mike/FBI-APPLE/FBI-APPLE2.csv", stringsAsFactors = FALSE)

Apple2_Neutral=Apple2[Apple2$Category=="Basic Neutral",]
Apple2_Positive=Apple2[Apple2$Category=="Basic Positive",]
Apple2_Negative=Apple2[Apple2$Category=="Basic Negative",]

```
## word cloud of Neutral words in Ashley madison incident
```{r,echo=FALSE}
df_clean <- wcloud_Ashley(Ash2_Neutral$Contents)
freq <- colSums(df_clean)
freq <- sort(freq,decreasing = T)
head(freq,50)
wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[50]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
```


## word cloud of Positive words in Ashley madison incident
```{r,echo=FALSE}
df_clean <- wcloud_Ashley(Ash2_Positive$Contents)
freq <- colSums(df_clean)
freq <- sort(freq,decreasing = T)
head(freq,50)
wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[50]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
```


## word cloud of Negative words in Ashley madison incident
```{r,echo=FALSE}
df_clean <- wcloud_Ashley(Ash2_Negative$Contents)
freq <- colSums(df_clean)
freq <- sort(freq,decreasing = T)
head(freq,50)
wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[50]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
```

## word cloud of Neutral words in Edward Snowden incident
```{r,echo=FALSE}
df_clean <- wcloud_Snowden(Snow2_Neutral$Contents)
freq <- colSums(df_clean)
freq <- sort(freq,decreasing = T)
head(freq,50)
wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[50]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
```


## word cloud of Positive words in Edward Snowden incident
```{r,echo=FALSE}
df_clean <- wcloud_Snowden(Snow2_Positive$Contents)
freq <- colSums(df_clean)
freq <- sort(freq,decreasing = T)
head(freq,50)
wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[50]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
```


## word cloud of Negative words in Edward Snowden incident
```{r,echo=FALSE}
df_clean <- wcloud_Snowden(Snow2_Negative$Contents)
freq <- colSums(df_clean)
freq <- sort(freq,decreasing = T)
head(freq,50)
wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[50]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
```

## word cloud of Neutral words in Celebrity Photo Hack incident
```{r,echo=FALSE}
df_clean <- wcloud_Celeb(Celeb2_Neutral$Contents)
freq <- colSums(df_clean)
freq <- sort(freq,decreasing = T)
head(freq,50)
wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[50]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
```


## word cloud of Positive words in Celebrity Photo Hack incident
```{r,echo=FALSE}

df_clean <- wcloud_Celeb(Celeb2_Positive$Contents)
 freq <- colSums(df_clean)
 freq <- sort(freq,decreasing = T)
 head(freq,50)
 wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[length(freq)]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
# }
```


## word cloud of Negative words in Celebrity Photo Hack incident
```{r,echo=FALSE}
df_clean <- wcloud_Celeb(Celeb2_Negative$Contents)
freq <- colSums(df_clean)
freq <- sort(freq,decreasing = T)
head(freq,50)
wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[50]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
```


## word cloud of Neutral words in FBI-APPLE incident
```{r,echo=FALSE}
df_clean <- wcloud_Apple(Apple2_Neutral$Contents)
freq <- colSums(df_clean)
freq <- sort(freq,decreasing = T)
head(freq,50)
wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[50]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
```


## word cloud of Positive words in FBI-APPLE incident
```{r,echo=FALSE}
df_clean <- wcloud_Apple(Apple2_Positive$Contents)
freq <- colSums(df_clean)
freq <- sort(freq,decreasing = T)
head(freq,50)
wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[50]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
```


## word cloud of Negative words in FBI-APPLE incident
```{r,echo=FALSE}
df_clean <- wcloud_Apple(Apple2_Negative$Contents)
freq <- colSums(df_clean)
freq <- sort(freq,decreasing = T)
head(freq,50)
wordcloud(words = names(freq),freq,min.freq = sort(freq,decreasing = T)[[50]],random.order = FALSE,random.color = TRUE,colors = brewer.pal(8, "Dark2"))
```